---
title: Cardiac pericytes contribute to myofibroblast expansion and vascular maturation
  following myocardial infarction
output: html_document
date: "2023-01-28"
---

```{r}
install.packages("/Users/mastorkia/Dropbox (EinsteinMed)/RISC_versions/RISC_1.6.0.tar.gz", repos = NULL, type = "source")
```


```{r, echo=F, message=F}
#Load needed libraries.
library(Seurat)
library(RISC)
library(data.table)
library(Matrix)
library(ggplot2)
library(RColorBrewer)
library(DoubletFinder)
library(dplyr)
library(edgeR)
library(ggalluvial)
```

```{r}
#Load matrices and start creating SEURAT objects necessary for double removal.
infart_sample_list <- c("Control1n2","Control3n4","Heart1n2","Heart3n4","Heart5")
```

```{r}
create_object<- function(sample_list){
  Dataset <- Read10X(data.dir =paste0("/path_to_cellranger_output/",sample_list, "_filtered_feature_bc_matrix/"))

  # Initialize the WT_object object with the raw (non-normalized data).
  Object <- CreateSeuratObject(counts = Dataset, project = paste0(sample_list), min.cells = 3, min.features = 200)

  Object[["percent.mt"]] <- PercentageFeatureSet(Object, pattern = "^mt-")

 png(file =paste0(sample_list,"_nCount_violin.png"),  
      width = 1000,
      height = 1200)
  counts_violin <- VlnPlot(Object, features = c("nFeature_RNA", "nCount_RNA", "percent.mt"), ncol = 3)

  print(counts_violin)
  dev.off()
  return(Object)
}
```


```{r}
Object_list <- mapply(FUN=create_object,infart_sample_list)
```

```{r}
#Filter each object accordingly.
Object_list$Control1n2 <- subset(Object_list$Control1n2, subset = nCount_RNA < 60000 & percent.mt < 10, nFeature_RNA > 2000)
Object_list$Control1n2

Object_list$Control3n4 <- subset(Object_list$Control3n4, subset = nCount_RNA < 50000 & percent.mt < 10, nFeature_RNA > 2000)
Object_list$Control3n4

Object_list$Heart1n2 <- subset(Object_list$Heart1n2, subset = nCount_RNA < 70000 & percent.mt < 10, nFeature_RNA > 2000)
Object_list$Heart1n2

Object_list$Heart3n4 <- subset(Object_list$Heart3n4, subset = nCount_RNA < 100000 & percent.mt < 10, nFeature_RNA > 2000)
Object_list$Heart3n4

Object_list$Heart5 <- subset(Object_list$Heart5, subset = nCount_RNA < 100000 & percent.mt < 10, nFeature_RNA > 2000)
Object_list$Heart5
```

```{r}
#Normalize and dim reduction to run Doublet finder.
normalize_function <- function(Object_list){
  Object_list <- NormalizeData(Object_list)
  Object_list <- FindVariableFeatures(Object_list, selection.method = "vst", nfeatures = 2000)
  Object_list <- ScaleData(Object_list)
  Object_list <- RunPCA(Object_list)
  Object_list <- FindNeighbors(Object_list, dims = 1:20)
  Object_list <- FindClusters(Object_list, resolution = 0.2)
  Object_list <- RunUMAP(Object_list, dims = 1:20)
}

Object_list <- mapply(FUN=normalize_function,Object_list)
```


```{r}
#Run the doubletfinder removal package.
#It need to be normalized by SCT.
doublet_finder <- function(seurat){
  seurat <- SCTransform(seurat)

  sweep.res.list <- paramSweep_v3(seurat, PCs = 1:20, sct = T)

  sweep.stats <- summarizeSweep(sweep.res.list, GT = FALSE)
  bcmvn <- find.pK(sweep.stats)
  maxscorepk <- bcmvn[bcmvn$BCmetric == max(bcmvn$BCmetric),2]
  maxscorepk <- as.numeric( levels(maxscorepk)[maxscorepk] )

  load("dratedf.rda")
  #And run linear regression to stimate drouplets based on number of cells.
  dbmodel <- lm(MultipletRate ~ CellsRecovered, data = dratedf)
  predicteddoubletrate <- as.numeric((dbmodel$coefficients['CellsRecovered'] * ncol(seurat)) + dbmodel$coefficients[1])

  homotypicprop <- modelHomotypic(as.vector(seurat@meta.data[,"seurat_clusters"]))
  nexppoi <- round(predicteddoubletrate * length(rownames(seurat@meta.data)))
  nexppoiadj <- round(nexppoi * (1 - homotypicprop))

  seurat <-doubletFinder_v3(seu = seurat, PCs = 1:20, pN = 0.25, pK = maxscorepk, nExp = nexppoiadj, sct = T)
}
```


```{r}
Object_list$Control1n2 <- doublet_finder(Object_list$Control1n2)

Object_list$Control3n4 <- doublet_finder(Object_list$Control3n4)

Object_list$Heart1n2 <- doublet_finder(Object_list$Heart1n2)

Object_list$Heart3n4 <- doublet_finder(Object_list$Heart3n4)

Object_list$Heart5 <- doublet_finder(Object_list$Heart5)
```

```{r}
#Remove the cells identified as doublets.
remove_doublets <- function(Object){
  no_double_cells <-Object@meta.data %>% filter(!.[[ncol(Object@meta.data)]]=="Doublet") %>% rownames()
  Object <- Object[,no_double_cells]
}

Object_list <- mapply(FUN=remove_doublets,Object_list)
```


```{r}
#Create RISC objects to run integration.
create_risc <- function(Object){
  #Now create RISC object with new matrix and coldata and save it.
  mat <- as.matrix(Object@assays$RNA@counts)#this step gices problem because of the size of the matrix. Has to be done in the server
  coldata <- Object@meta.data
  rowdata <- data.frame(Symbol = rownames(mat), row.names = rownames(mat))
  Object <- readsc(mat, coldata, rowdata, is.filter = T)
  return(Object)
}

```

```{r}
Object_RISC <- mapply(FUN=create_risc,Object_list)
```

#Save all the filtered RISC objects
```{r}
save_risc <- function(object,infart_sample_list){
  saveRDS(object, file = paste0("RISC_Objects/",infart_sample_list, "_RISC.rds"))
}
mapply(FUN=save_risc,Object_RISC,infart_sample_list)
```

#Normalize and find variable genes.
```{r}
process0 <- function(obj0){
  #Filter. It is necessary again
  obj0 = scFilter(obj0, min.UMI = 10, max.UMI = Inf, min.gene = 1, min.cell = 1)
  # Normalize the raw counts
  obj0 = scNormalize(obj0, ncore = 4)
  # Find highly variable genes
  obj0 = scDisperse(obj0)
  # print(length(obj0@vargene))
  return(obj0)
}
```

```{r}
Object_RISC <- mapply(FUN=process0,Object_RISC)
```

```{r}
#Check which of the datatsets to use as reference.
var0 = Reduce(
  intersect, list(
  Object_RISC$Control1n2@rowdata$Symbol, Object_RISC$Control3n4@rowdata$Symbol, Object_RISC$Heart1n2@rowdata$Symbol, Object_RISC$Heart3n4@rowdata$Symbol,
Object_RISC$Heart5@rowdata$Symbol 
  )
)

InPlot(Object_RISC, var.gene = var0, Std.cut = 0.99, ncore = 4, minPC = 16, nPC = 20)
```

#Use Heart1n2 woukd be the reference.
```{r}
set.seed(123)
#List to integrate the data. In this case we use Heart1n2 as reference.
Merge_list = list(Object_RISC$Heart1n2, Object_RISC$Heart3n4, Object_RISC$Heart5, Object_RISC$Control3n4, Object_RISC$Control1n2)
```


```{r}
#Integrate 
Integration_Ids <- c("Heart1n2", "Heart3n4", "Heart5", "Control3n4", "Control1n2")
Merge_Object = scMultiIntegrate(
  objects = Merge_list, eigens = 20, add.Id = Integration_Ids, var.gene = var0,
align = 'OLS', npc = 50, adjust = TRUE, ncore = 4
)
```


```{r}
#Add condition colunm.
Merge_Object@coldata <- Merge_Object@coldata %>% rename(Condition=Set)
Merge_Object@coldata <- Merge_Object@coldata %>% rename(Set=orig.ident)

Merge_Object@coldata$Condition <- as.character(Merge_Object@coldata$Condition)
Merge_Object@coldata$Condition[Merge_Object@coldata$Condition=="Heart1n2"] <- "Infart"
Merge_Object@coldata$Condition[Merge_Object@coldata$Condition=="Heart3n4"] <- "Infart"
Merge_Object@coldata$Condition[Merge_Object@coldata$Condition=="Heart5"] <- "Infart"
Merge_Object@coldata$Condition[Merge_Object@coldata$Condition=="Control1n2"] <- "Control"
Merge_Object@coldata$Condition[Merge_Object@coldata$Condition=="Control3n4"] <- "Control"
```


```{r}
saveRDS(Merge_Object, file = paste0("RISC_Objects/Merged_RISC.rds"))
```


```{r}
#Run UMAP reduction and clustering
Merge_Object = scPCA(Merge_Object, npc = 20)
Merge_Object = scUMAP(Merge_Object, npc = 20, use = "PLS")
Merge_Object = scCluster(Merge_Object, slot = "cell.pls", neighbor = 12, method = "louvain", npc = 20)
print(table(Merge_Object@coldata$Cluster))
```

```{r}
DimPlot(Merge_Object, slot = "cell.umap", colFactor = "Cluster")
```



```{r}
#Subset each sample and plot integration.
plot_each_samples <- function(sample){
  sample_cells <- Merge_Object@coldata %>% filter(orig.ident==sample) %>% rownames()
  subset_object <- SubSet(Merge_Object, cells = sample_cells)
  png(file =paste0("Figures/",sample, "_Integration.png"),  
    width = 800,
    height = 800)
  plot <- DimPlot(subset_object, slot = "cell.umap", colFactor = "Cluster")
  print(plot)
  dev.off()
}
```

```{r}
plot_each_samples("Heart1n2")
plot_each_samples("Heart3n4")
plot_each_samples("Heart5")
plot_each_samples("Control3n4")
plot_each_samples("Control1n2")

```

#Since we have a separated cluster (of 31 cells) we need to remove it from the beginning and rerun everything. Will do this manually using UMAP coordinates. 
```{r}
umap_first_integration <- as.data.frame(Merge_Object@DimReduction$cell.umap)

cell_to_remove <- umap_first_integration %>% filter(UMAP2 < -20) %>% rownames()
```

```{r}
Object_RISC2 <- Object_RISC
```

#Subset these cells from object.
```{r}
remove <- cell_to_remove[grep("Heart1n2",cell_to_remove)]
remove<- stringr::str_remove(remove, "Heart1n2_")
all_cells <- rownames(Object_RISC2$Heart1n2@coldata)
keep <- all_cells[!(all_cells %in% remove)]
Object_RISC2$Heart1n2 <- SubSet(Object_RISC2$Heart1n2, cells = keep)

remove <- cell_to_remove[grep("Heart3n4",cell_to_remove)]
remove<- stringr::str_remove(remove, "Heart3n4_")
all_cells <- rownames(Object_RISC2$Heart3n4@coldata)
keep <- all_cells[!(all_cells %in% remove)]
Object_RISC2$Heart3n4 <- SubSet(Object_RISC2$Heart3n4, cells = keep)

remove <- cell_to_remove[grep("Heart5",cell_to_remove)]
remove<- stringr::str_remove(remove, "Heart5_")
all_cells <- rownames(Object_RISC2$Heart5@coldata)
keep <- all_cells[!(all_cells %in% remove)]
Object_RISC2$Heart5 <- SubSet(Object_RISC2$Heart5, cells = keep)

remove <- cell_to_remove[grep("Control1n2",cell_to_remove)]
remove<- stringr::str_remove(remove, "Control1n2_")
all_cells <- rownames(Object_RISC2$Control1n2@coldata)
keep <- all_cells[!(all_cells %in% remove)]
Object_RISC2$Control1n2 <- SubSet(Object_RISC2$Control1n2, cells = keep)

remove <- cell_to_remove[grep("Control3n4",cell_to_remove)]
remove<- stringr::str_remove(remove, "Control3n4_")
all_cells <- rownames(Object_RISC2$Control3n4@coldata)
keep <- all_cells[!(all_cells %in% remove)]
Object_RISC2$Control3n4 <- SubSet(Object_RISC2$Control3n4, cells = keep)

```


#Rerun integration again.
```{r}
process0 <- function(obj0){
  #Filter. It is necessary again
  obj0 = scFilter(obj0, min.UMI = 10, max.UMI = Inf, min.gene = 1, min.cell = 1)
  # Normalize the raw counts
  obj0 = scNormalize(obj0, ncore = 4)
  # Find highly variable genes
  obj0 = scDisperse(obj0)
  # print(length(obj0@vargene))
  return(obj0)
}

Object_RISC2 <- mapply(FUN=process0,Object_RISC2)
```
#Lets start with the integration.
```{r}
var0 = Reduce(
intersect, list(
  Object_RISC2$Control1n2@rowdata$Symbol, Object_RISC2$Control3n4@rowdata$Symbol, Object_RISC2$Heart1n2@rowdata$Symbol, Object_RISC2$Heart3n4@rowdata$Symbol,
Object_RISC2$Heart5@rowdata$Symbol 
  )
)

InPlot(Object_RISC2, var.gene = var0, Std.cut = 0.99, ncore = 4, minPC = 16, nPC = 20)
```


```{r}
set.seed(123)
#Use Heart1n2 as reference.
Merge_list = list(Object_RISC2$Heart1n2, Object_RISC2$Heart3n4, Object_RISC2$Heart5, Object_RISC2$Control3n4, Object_RISC2$Control1n2)
```

#Integrate again.
```{r}
Integration_Ids <- c("Heart1n2", "Heart3n4", "Heart5", "Control3n4", "Control1n2")
Merge2_Object = scMultiIntegrate(
  objects = Merge_list, eigens = 20, add.Id = Integration_Ids, var.gene = var0,
align = 'OLS', npc = 50, adjust = TRUE, ncore = 4
)
```

#Create a condition colunm.
```{r}
Merge2_Object@coldata <- Merge2_Object@coldata %>% rename(Condition=Set)
Merge2_Object@coldata <- Merge2_Object@coldata %>% rename(Set=orig.ident)
Merge2_Object@coldata$Condition <- as.character(Merge2_Object@coldata$Condition)
Merge2_Object@coldata$Condition[Merge2_Object@coldata$Condition=="Heart1n2"] <- "Infart"
Merge2_Object@coldata$Condition[Merge2_Object@coldata$Condition=="Heart3n4"] <- "Infart"
Merge2_Object@coldata$Condition[Merge2_Object@coldata$Condition=="Heart5"] <- "Infart"
Merge2_Object@coldata$Condition[Merge2_Object@coldata$Condition=="Control1n2"] <- "Control"
Merge2_Object@coldata$Condition[Merge2_Object@coldata$Condition=="Control3n4"] <- "Control"

saveRDS(Merge2_Object, file = paste0("RISC_Objects/Merged2_RISC.rds"))
```


```{r}
#Run UMAP reduction.
Merge2_Object = scUMAP(Merge2_Object, npc = 20, use = "PLS")

Merge2_Object = scCluster(Merge2_Object, slot = "cell.pls", neighbor = 12, method = "louvain", npc = 20)
print(table(Merge2_Object@coldata$Cluster))

DimPlot(Merge2_Object, slot = "cell.umap", colFactor = "Cluster")
```


```{r}
#In order to plot Control and Hearts UMAP I need to subset the data. Cluster 2 is not present in Contorl so it will fail when plotting by colors. Change one of the cells in Control to Cluster 2.
Merge2_Object@coldata["Control1n2_GCCAGCATCGATTCCC-1",]$Cluster <- 2
Merge2_Object@coldata["Control3n4_TGAGCGCAGAAGCCTG-1",]$Cluster <- 2
```


#Subset each sample and plot integration.
```{r}
plot_each_samples <- function(sample){
  sample_cells <- Merge2_Object@coldata %>% filter(Set %in% sample) %>% rownames()
  subset_object <- SubSet(Merge2_Object, cells = sample_cells)
  png(file =paste0("Integration2_Figures/",sample, "_Integration2_new_colors.png"),  
    width = 800,
    height = 800)
  plot <- RISC::DimPlot(subset_object, slot = "cell.umap", colFactor = "Cluster", Colors = c("#00008b", "gray", "#00BA38", "#00BFC4", "#C77CFF", "brown", "#7CAE00", "#F8766D", "#F564E3", "#fadadd", "#B79F00", "#DE8C00"))
  print(plot)
  dev.off()
}
```

```{r}
plot_each_samples("Heart1n2")
plot_each_samples("Heart3n4")
plot_each_samples("Heart5")
plot_each_samples("Control3n4")
plot_each_samples("Control1n2")
plot_each_samples(c("Control1n2","Control3n4"))
plot_each_samples(c("Heart1n2","Heart3n4","Heart5"))

```


#Run marker identification for each cluster.
```{r}
Integrated2_markers <- AllMarker(
    Merge2_Object,
    positive = FALSE,
    frac = 0.25,
    log2FC = 0.25,
    Padj = 0.01,
    latent.factor = NULL,
    min.cells = 25L,
    method = "Wilcox",
    ncore = 1
)
write.csv(Integrated2_markers, "Integrated2_marker_df/Integrated2_markers.csv", row.names = F)
```

#Plot top markers.
```{r}
integration_draw_heatmap <- function(dataframe,obejct){
  pdf(file =paste0("Integration2_Figures/Integration2_top10markers_heatmap.pdf"),  
      width = 8,
      height = 15)
  dataframe %>%
    group_by(Cluster) %>%
    top_n(n = 10, wt = log2FC) -> top5
  plot <- Heat(obejct, colFactor = "Cluster",genes  = top5$Symbol, smooth="smooth", gene.lab = T,  num=10, gene.lab.size = 10) 
  print(plot)
  dev.off()
}
integration_draw_heatmap(Integrated2_markers,Merge2_Object)
```

#Plot markers of interest.
```{r}
markers_to_plot_2 <- c("Cspg4","Myh11","Acta2","Mylk","Myl9","Smtn","Tagln","Mcam","Pdgfrb","Cspg4", "Rgs5" ,"Vtn","Ifitm1","Kcnj8","Cd248","Anpep", "Des", "Dlk1", "Zic1", "Abcc9", "Notch3","Pdgfra" , "Tcf21", "Col1a1", "Col3a1","Fbln1", "Fbln2", "Loxl1", "Postn" , "Acta2" , "S100a4", "Fap","Vim" ,"Ptprc" , "Cdh5", "Adgre1" ,"Tnnt1", "Tnnt2", "Actc1", "Myh7") 
```

```{r}
Heat(Merge2_Object, colFactor = "Cluster",genes  = markers_to_plot_2, smooth="smooth", gene.lab = T,  num=10, gene.lab.size = 10) 
```

#Count number of cells in each cluster for each sample
```{r}
Merge2_metadata <- Merge2_Object@coldata
clusters <- unique(Merge2_metadata$Cluster)
Set_cluster_number <- data.frame(Var1=clusters)
for ( i in unique(Merge2_metadata$Set)){
  Merge2_metadata_set <- Merge2_metadata %>% filter(Set==i)
  cluster_table <- as.data.frame(table(Merge2_metadata_set$Cluster))
  cluster_table <- cluster_table %>% dplyr::rename(!!paste0(i) := Freq)
  Set_cluster_number <- join(Set_cluster_number,cluster_table, type="inner")
}
Set_cluster_number <- Set_cluster_number %>% dplyr::rename(Cluster = Var1)
write.csv(Set_cluster_number, "Integrated2_marker_df/Sample_cluster_number.csv", row.names = F)
```

#Run DE analysis for each of the Clusters.
```{r}
DE_function <- function(reference, case){
  DE <- data.frame()
  for (celltype in unique(Merge2_Object@coldata$Cluster)){
    tryCatch ( {
      cell1 = rownames(Merge2_Object@coldata)[Merge2_Object@coldata$Cluster == celltype & Merge2_Object@coldata$Condition %in% reference]
      cell2 = rownames(Merge2_Object@coldata)[Merge2_Object@coldata$Cluster == celltype & Merge2_Object@coldata$Condition %in% case]
      DE0 = scDEG(Merge2_Object, cell.ctrl = cell1, cell.sam = cell2, ncore = 4, frac = 0.1, Padj = 0.05, log2FC = 0.25, method = "Wilcox")
      Cluster <- data.frame(Cluster=rep(paste0(celltype), nrow(DE0)))
      DE1 <- cbind(DE0,Cluster)
      DE <- rbind(DE,DE1)
    },error=function(e){cat("ERROR :",conditionMessage(e), "\n")} )
  }
return(DE)
}
```

```{r}
Nikolaos_Integrated2_DE <- DE_function("Control","Infart")
```


#Run DE as pseudo-bulk RNAseq using edgeR. For that create a new count table summing cells coming from same sample. Since RISC doesnt save raw data go back to seurat and subset the data again.
#Raw counts (doublets are removed). We need to remove only those cells that were in a separated cluster.
```{r}
raw_control1n2 <- Object_list$Control1n2@assays$RNA@counts
raw_control3n4 <- Object_list$Control3n4@assays$RNA@counts
raw_heart1n2 <- Object_list$Heart1n2@assays$RNA@counts
raw_heart3n4 <- Object_list$Heart3n4@assays$RNA@counts
raw_heart5 <- Object_list$Heart5@assays$RNA@counts
```

#metadata to get cells for each cluster.
```{r}
Merge2_metadata <- Merge2_Object@coldata
```

#Create function to remove cells and then get a df with sample and celltype.
```{r}
pseudo_bulk_df <- function(sample,raw_counts_sample){
  remove <- cell_to_remove[grep(paste0(sample,"_"),cell_to_remove)]
  remove<- stringr::str_remove(remove, paste0(sample,"_"))
  raw_counts_sample <- raw_counts_sample[, !(colnames(raw_counts_sample) %in% remove)]
  subset_metadata <- Merge2_metadata %>% filter(Set==sample)
  sample_pseudo_bulk <- as.data.frame(rownames(raw_counts_sample))
    for ( i in unique(subset_metadata$Cluster)){
      cell_clusters <- subset_metadata %>% filter(Cluster==i) %>% select(scBarcode)
      cell_clusters <- cell_clusters$scBarcode
      if( isTRUE(length(cell_clusters) > 1)){
        subseted_raw <- raw_counts_sample[,cell_clusters]
        #subseted_raw <- as.data.frame(subseted_raw)
        Cluster_sum <- as.data.frame(rowSums(subseted_raw))
        Cluster_sum <- Cluster_sum %>% dplyr::rename(!!paste0(sample,"_Cluster",i) := 1)
        rownames(Cluster_sum) <- NULL
        #print(colnames(Cluster_sum))
        sample_pseudo_bulk <- cbind(sample_pseudo_bulk,Cluster_sum)
        }
    }
  return(sample_pseudo_bulk)
}
```

```{r}
Control1n2_pseudo_bulk <- pseudo_bulk_df("Control1n2", raw_control1n2)

Control3n4_pseudo_bulk <- pseudo_bulk_df("Control3n4", raw_control3n4)

Heart1n2_pseudo_bulk <- pseudo_bulk_df("Heart1n2", raw_heart1n2)

Heart3n4_pseudo_bulk <- pseudo_bulk_df("Heart3n4", raw_heart3n4)

Heart5_pseudo_bulk <- pseudo_bulk_df("Heart5", raw_heart5)

```

```{r}
#Now bind all df
all_psuedo_list <- list(Control1n2_pseudo_bulk,Control3n4_pseudo_bulk,Heart1n2_pseudo_bulk,Heart3n4_pseudo_bulk,Heart5_pseudo_bulk)
```

```{r}
all_pseudo_bulk_counts <- join_all(all_psuedo_list,type = "full", match = "all")
all_pseudo_bulk_counts[is.na(all_pseudo_bulk_counts)] <- 0
rownames(all_pseudo_bulk_counts) <- all_pseudo_bulk_counts$`rownames(raw_counts_sample)`
all_pseudo_bulk_counts$`rownames(raw_counts_sample)` <- NULL
write.csv(all_pseudo_bulk_counts, "Pseudo_bulk_raw_counts.csv", row.names = T)
```

```{r}
#Remove Cluster2, Cluster7, Cluster8  Cluster9 and Cluster11 because tehere is not enougth data for Controls.
subset_pseudo_bulk <- all_pseudo_bulk_counts %>% select(-contains(c("Cluster2","Cluster7","Cluster8","Cluster9", "Cluster11")))

```

#Create function to run edgeR for each Cluster.
https://bioconductor.org/packages/release/bioc/vignettes/edgeR/inst/doc/edgeRUsersGuide.pdf

```{r}
edgeR_cluster <- function(Cluster_name){
  subset2_pseudo_bulk <- subset_pseudo_bulk %>% select(ends_with(Cluster_name))
  Sample_name <- colnames(subset2_pseudo_bulk)
  Cluster_number <- vapply(strsplit(Sample_name, "_", fixed = TRUE), "[", "", 2)
  Condition <- gsub("[0-9].*","",Sample_name)
  pseud_bulk_md <- data.frame(Sample_name,Cluster_number,Condition)
  rownames(pseud_bulk_md) <- pseud_bulk_md$Sample_name
  pseud_bulk_md$Condition <- as.factor(pseud_bulk_md$Condition)
  y <- DGEList(counts = subset2_pseudo_bulk, group = pseud_bulk_md$Condition)
  keep <- filterByExpr(y)
  y <- y[keep, , keep.lib.sizes=FALSE]
  y <- calcNormFactors(y)
  design <- model.matrix(~pseud_bulk_md$Condition)
  y <- estimateDisp(y,design)
  fit <- glmQLFit(y, design, robust = TRUE)
  fit <- glmQLFTest(fit, coef=2)
  results <- as.data.frame(topTags(fit, n=2000))
  results$Gene <- as.character(rownames(results))
  results <- results %>% arrange((FDR))
  results <- results %>% select(Gene, everything())
  Cluster <- data.frame(Cluster=rep(paste0(Cluster_name), nrow(results)))
  results <- cbind(results,Cluster)
  return(results)
}

```

```{r}
Cluster1_pseudo_bulk_DE <- edgeR_cluster("Cluster1")
Cluster3_pseudo_bulk_DE <- edgeR_cluster("Cluster3")
Cluster4_pseudo_bulk_DE <- edgeR_cluster("Cluster4")
Cluster5_pseudo_bulk_DE <- edgeR_cluster("Cluster5")
Cluster6_pseudo_bulk_DE <- edgeR_cluster("Cluster6")
Cluster10_pseudo_bulk_DE <- edgeR_cluster("Cluster10")
Cluster12_pseudo_bulk_DE <- edgeR_cluster("Cluster12")

```


```{r}
pseudo_bulk_de_list <-list( Cluster1_pseudo_bulk_DE,Cluster3_pseudo_bulk_DE,Cluster4_pseudo_bulk_DE,Cluster5_pseudo_bulk_DE,Cluster6_pseudo_bulk_DE,Cluster10_pseudo_bulk_DE,Cluster12_pseudo_bulk_DE)
DE_psuedo_bulk <- do.call(rbind,pseudo_bulk_de_list)
```

```{r}
write.csv(DE_psuedo_bulk, "DE2_psuedo_bulk_Infart.csv", row.names = T, col.names = T)
```

# 2 UMAP from controls samples and infarts.
```{r}
for(i in unique(Merge2_Object@coldata$Condition)){
  sample_cells <- Merge2_Object@coldata %>% filter(Condition==i) %>% rownames()
  subset_object <- SubSet(Merge2_Object, cells = sample_cells)
  png(file =paste0("Integration2_Figures/",i, "_Integration2.png"),  
    width = 800,
    height = 800)
  plot <- DimPlot(subset_object, slot = "cell.umap", colFactor = "Cluster")
  plot <- plot + ggtitle(paste0(i, " hearts UMAP"))
  print(plot)
  dev.off()
}
```

```{r}
#UMAP coordinates to run scvelo and cellrank.
metadata_file <- Merge2_Object@coldata
metadata_file$UMAP1 <- (Merge2_Object@DimReduction$cell.umap)[,1]
metadata_file$UMAP2 <- (Merge2_Object@DimReduction$cell.umap)[,2]
write.csv(metadata_file, "Infart_RISC_metadata.csv")
```


```{r}
#Plot top 5 markers data.
Integrated2_markers %>%
  group_by(Cluster) %>%
  top_n(n = 5, wt = log2FC) -> Integrated2_markers_top5

colors_for_paper=list(c("1"="#00008b", "2"="gray", "3"="#00BA38", "4"="#00BFC4","5"= "#C77CFF","6"= "brown","7"= "#7CAE00","8"= "#F8766D","9"= "#F564E3","10"= "#fadadd","11"= "#B79F00","12"= "#DE8C00"))

Heat(Merge2_Object, colFactor = "Cluster",genes  = Integrated2_markers_top5$Symbol, smooth="smooth", gene.lab = T,  num=10, gene.lab.size = 10, ann_col=colors_for_paper)
```

